Solving an Exam Scheduling Problem Using a Genetic Algorithm

### 2009-11-24 trunk/Paper/paper.tex

\section{The Problem}
Description of our problem

>>>>

\begin{abstract}
  This concise, one-paragraph summary should describe the general thesis
  and conclusion of your paper. A reader should be able to learn the purpose
  of the paper and the reason for its importance from the abstract.
\end{abstract}

\section{The Problem}
  Consider a university, with all of its students, courses and classrooms. 
  How does one try to build the best possible schedule for an exam session? 
  A good schedule is a schedule where:
  \begin{itemize}
  \item  There are no conflicts, such as two different exams in the same room
         at the same, or a student having two different exams at the same time.
  \item  Students don't have too many exams in a very short time.
  \item  It is bad for a room to have two exams directly one after another,
         as it doesn't give time for teachers and TAs to set up the room.
  \end{itemize}

 Considering a huge university like University of Toronto, with its 70000 students
 and numerous courses, making a good schedule by hand would be very tedious.
